---
output:
  github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Build Status](https://travis-ci.org/noamross/rchie.svg?branch=master)](https://travis-ci.org/noamross/rchie)
[![Build status](https://ci.appveyor.com/api/projects/status/osig88jvixel2taa/branch/master?svg=true)](https://ci.appveyor.com/project/NoamRoss/rchie/branch/master)
[![codecov.io](https://codecov.io/github/noamross/rchie/coverage.svg?branch=master)](https://codecov.io/github/noamross/rchie?branch=master)


# An R parser for ArchieML

This package is a wrapper for [archieml-js](https://github.com/newsdev/archieml-js),
a parser for the New York Times' [ArchieML](http://archieml.org/) format.  ArchieML is designed
to include structured data in free-form documents.

Right now it just has one function, `from_aml`, which loads ArchieML data from a string, file, or URL.

archieml-js (included under `inst`, using `git subtree`) parses ArchieML to JSON.  It is run using V8, and then the JSON data is imported via jsonlite.


## Install

Note that, because it uses the V8 package, rchie has a system requirement of libv8.

```
library(devtools)
install_github('noamross/rchie')
```

## Usage

`from_aml` can read ArchieML from a string, file, or URL:

```{r}
library(rchie)
data1 <- "
  [arrayName]
  
  Jeremy spoke with her on Friday, follow-up scheduled for next week
  name: Amanda
  age: 26
  
  # Contact: 434-555-1234
  name: Tessa
  age: 30
  
  []
  "

from_aml(data1)
from_aml("http://archieml.org/test/1.0/arrays.1.aml")
```

Note that you can pass arguments through `from_aml` to `jsonlite::fromJSON` to
determine how JSON is converted to R objects:

```{r}
from_aml(data1, simplifyVector = FALSE)
```

See http://archieml.org/ for more examples of ArchieML


